---
title: "Homework 9"
author: "Nancy Yeung (ny3257) - SDS 315 - [GitHub Repository](https://github.com/0NancyYeung0/Homework9.git)"
output: pdf_document
---
\vspace{-1cm}

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=3, fig.width=8, warning=FALSE, message=FALSE, echo=FALSE)
```

```{r}
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(kableExtra)
library(knitr)
library(tidyverse)
library(mosaic)
library(MatchIt)
Turnout <- read.csv("turnout.csv")
Solder <- read.csv("solder.csv")
```
------------------------------------------------------------------------
\begingroup
\fontsize{12}{14}\selectfont
**Problem 1: Get Out the Vote**
\endgroup

\begingroup
\fontsize{10}{12}\selectfont
**Part A:**
\endgroup

```{r}
GotCall <- Turnout %>%
  filter(GOTV_call == 1)
Voted <- GotCall %>%
  filter(voted1998 == 1)

Prop1 <- nrow(Voted) / nrow(GotCall)

NoCall <- Turnout %>%
  filter(GOTV_call == 0)
Voted2 <- NoCall %>%
  filter(voted1998 == 1)
Prop2 <- nrow(Voted2) / nrow(NoCall)

Conf <- prop.test(voted1998 ~ GOTV_call, data = Turnout)
```

The proportion of people who received a GOTV call and voted in 19998 is `r round(Prop1, 4)`, and the proportion of those who didn't get a call and voted was `r round(Prop2, 4)`.

The large-sample 95% confidence interval for the difference in proportions of voting in 1998 between individuals who received a GOTV call and those who didn't is (0.1411, 0.2659). This means that we are 95% confident that the true difference in proportions falls within this interval. The proportion of voting in 1998 for those who received a GOTV call is estimated to be 0.5558, while for those who didn't receive a GOTV call, it is estimated to be 0.3522.

\begingroup
\fontsize{10}{12}\selectfont
**Part B:**
\endgroup

```{r}
ggplot(Turnout) + 
  geom_bar(aes(x = factor(GOTV_call), y = voted1998, fill = factor(MAJORPTY)), stat = "identity") +
  facet_wrap(~MAJORPTY, labeller = labeller(MAJORPTY = c('0' = '', '1' = ''))) + 
  labs(title = 'Voter Turnout in 1998 by if They Got a Call and Political Party Registration', x = 'Got Call to Vote', y = 'Number of Voters in 1998', fill = 'Political Party') + 
  scale_fill_manual(name = 'Registered to Major Party', labels = c('No', 'Yes'), values = c('pink', 'skyblue')) + 
  scale_x_discrete(labels = c('No', 'Yes')) +  # Set x-axis labels
  theme_minimal() + 
  theme(text = element_text(size = 13, family = "serif"))
```

The graph above shows that individuals registered to a major political party were more likely to receive a call to vote before the 1998 election and to participate in the election itself. This observation indicates that the MAJORPTY variable acts as a confounder in the analysis.

```{r}
ggplot(Turnout, aes(x = factor(voted1998), y = AGE, fill = factor(GOTV_call))) +
  geom_boxplot() +
  labs(title = "Voter Turnout in 1998 by if They Got a Call and Age",
       x = "Voted in 1998", y = "Age",
       fill = "GOTV Call") +
  scale_fill_manual(name = "GOTV Call", labels = c("No", "Yes"), values = c("skyblue", "pink")) + 
  scale_x_discrete(labels = c('No', 'Yes')) +  # Set x-axis labels
  theme_minimal() + 
  theme(text = element_text(size = 13, family = "serif"))
```

The graph above shows that individuals who were older were more likely to receive a call to vote before the 1998 election and to participate in the election itself. This observation indicates that the AGE variable acts as a confounder in the analysis.

```{r}
ggplot(Turnout) + 
  geom_bar(aes(x = factor(GOTV_call), y = voted1998, fill = factor(voted1996)), stat = "identity") +
  facet_wrap(~voted1996, labeller = labeller(voted1996 = c('0' = '', '1' = ''))) + 
  labs(title = 'Voter Turnout in 1998 by if They Got a Call and if They Voted in 1996', x = 'Got Call to Vote', y = 'Number of Voters in 1998', fill = 'Voted in 1996') + 
  scale_fill_manual(name = 'Voted in 1996', labels = c('No', 'Yes'), values = c('pink', 'skyblue')) + 
  scale_x_discrete(labels = c('No', 'Yes')) +  # Set x-axis labels
  theme_minimal() + 
  theme(text = element_text(size = 13, family = "serif"))
```

The graph above shows that individuals who voted in 1996 were more likely to receive a call to vote before the 1998 election and to participate in the election itself. This observation indicates that the voted1996 variable acts as a confounder in the analysis.

\begingroup
\fontsize{10}{12}\selectfont
**Part C:**
\endgroup

```{r}
Matched <- matchit(GOTV_call ~ factor(voted1996) + AGE + factor(MAJORPTY), data = Turnout, ratio = 5) %>%
  match.data()

Table1 <- xtabs(~ voted1996 + GOTV_call, data = Matched) %>%
                      prop.table(margin=2)
kable(Table1, caption = "Contingency Table 1: Voted in 1996 vs. GOTV Call", align = "c", booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "hold_position"))

Table2 <- mean(AGE ~ GOTV_call, data = Matched)
kable(Table2, caption = "Contingency Table 2: Age vs. GOTV Call", align = "c", booktabs = T, col.names = c("Mean")) %>% 
  kable_styling(latex_options = c("striped", "hold_position"))

Table3 <- xtabs(~ MAJORPTY + GOTV_call, data = Matched) %>%
  prop.table(margin=2)
kable(Table3, caption = "Contingency Table 3: Registered to Major Party vs. GOTV Call", align = "c", booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "hold_position"))

GotCallMatched <- Matched %>%
  filter(GOTV_call == 1)
GotCallVoteMatched <- GotCallMatched %>%
  filter(voted1998 == 1)
GotCallVotePropMatched = nrow(GotCallVoteMatched) / nrow(GotCallMatched)

NoCallMatched <- Matched %>%
  filter(GOTV_call == 0)
NoCallVoteMatched <- NoCallMatched %>%
  filter (voted1998 == 1)
NoCallVotePropMatched <- nrow(NoCallVoteMatched) / nrow(NoCallMatched)

PartC <- prop.test(voted1998 ~ GOTV_call, data = Matched)
```

In the tables above 0 indicates a no and 1 a yes. As seen in the three Contingency Tables above the proportions of if they voted in 1996, age, and major party registration appear balanced with if they got a GOTV call, therefore showing that "matched" data is balanced.

The proportion of individuals who received a GOTV call and voted in 1998 is approximately `r round(GotCallVotePropMatched, 4)` The sample proportion of individuals who did not receive a GOTV call and voted in 1998 is approximately `r round(NoCallVotePropMatched, 4)`. The large-sample 95% confidence interval for the difference in these proportions is (0.0056, 0.1418). The GOTV call appear to have a positive effect on the likelihood of voting in the 1998 election. 

\newpage

\begingroup
\fontsize{12}{14}\selectfont
**Problem 2: Manufacturing flaws in circuit boards**
\endgroup

\begingroup
\fontsize{10}{12}\selectfont
**Part A:**
\endgroup

```{r}
ggplot(Solder) + 
  geom_boxplot(aes(x = Opening, y = skips, fill = factor(Opening)), position = "dodge") +
  facet_grid(. ~ Opening, scales = "free_x", space = "free_x", labeller = labeller(Opening = c('L' = '', 'M' = '', 'S' = ''))) + 
  labs(title = 'Opening Type vs. Number of Skips', x = 'Opening Type', y = 'Number of Skips', fill = 'Opening Type') + 
  scale_fill_manual(name = 'Opening Type', labels = c('Large', 'Medium', 'Small'), values = c('skyblue', 'pink', 'violet')) +
  scale_x_discrete(labels = c('', '', '')) +  # Set x-axis labels
  theme_minimal() + 
  theme(text = element_text(size = 13, family = "serif"))
```

The graph above shows different opening types and the range of the number of skips on the circuit board.

```{r}
ggplot(Solder) + 
  geom_boxplot(aes(x = Solder, y = skips, fill = factor(Solder)), position = "dodge") +
  facet_grid(. ~ Solder, scales = "free_x", space = "free_x", labeller = labeller(Solder = c('Thick' = '', 'Thin' = ''))) + 
  labs(title = 'Solder Type vs. Number of Skips', x = 'Solder Type', y = 'Number of Skips', fill = 'Opening Type') + 
  scale_fill_manual(name = 'Solder Type', labels = c('Thick', 'Thin'), values = c('skyblue', 'pink')) +
  scale_x_discrete(labels = c('', '')) +  # Set x-axis labels
  theme_minimal() + 
  theme(text = element_text(size = 13, family = "serif"))
```

The graph above shows different solder types and the range of the number of skips on the circuit board.

\begingroup
\fontsize{10}{12}\selectfont
**Part B:**
\endgroup

```{r}
RMSkips <- lm(skips ~ Opening:Solder + Solder + Opening, data = Solder) 
RMSkipsCoef <- coef(RMSkips) 

RMSkipsCoef <- as.data.frame(RMSkipsCoef)

row.names(RMSkipsCoef) <- c("Thick Solder & Large Opening", "Thin Solder", "Medium Opening", "Small Opening", "Medium Opening + Thin Solder", "Small Opening + Thick Solder")

kable(RMSkipsCoef, booktabs = TRUE, col.names = c("Coefficient Value")) %>%
  kable_styling(latex_options = c("striped", "hold_position"))

RMSkips <- confint(RMSkips, level = 0.95)
row.names(RMSkips) <- c("Thick Solder & Large Opening", "Thin Solder", "Medium Opening", "Small Opening", "Medium Opening + Thin Solder", "Small Opening + Thick Solder")
kable(RMSkips, booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "hold_position"))
```

\newpage

\begingroup
\fontsize{10}{12}\selectfont
**Part C:**
\endgroup

1. Thick Solder & Large Opening: Holding all other variables constant, the baseline expected change in the number of skips for circuit boards with thick solder and large opening is approximately 0.39.
2. Thin Solder: Holding all other variables constant, the expected change in the number of skips for circuit boards with thin solder in isolation is approximately 2.28.
3. Medium Opening: Holding all other variables constant, the expected change in the number of skips for circuit boards with a medium-sized opening in isolation is approximately 2.41.
4. Small Opening: Holding all other variables constant, the expected change in the number of skips for circuit boards with a small opening in isolation is approximately 5.13.
5. Medium Opening + Thin Solder: Holding all other variables constant, the expected change in the number of skips for circuit boards with a medium-sized opening and thin solder is approximately -0.74.
6. Small Opening + Thick Solder: Holding all other variables constant, the expected change in the number of skips for circuit boards with a small opening and thick solder is approximately 9.65.

\begingroup
\fontsize{10}{12}\selectfont
**Part D:**
\endgroup

I would recommend medium opening with a thin solder. The coefficient of -0.74 has the lowest estimated number of skips among all combinations.
